Importance of Sampling Frequency in the Dynamic Speckle Analysis

### 2019-04-04 article/article_1.tex
acabe de escribir primera version, pero falta agregar un grafico.

\begin{abstract}
In this article, we show as the variation of sampling frequency, 
in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
in this case: the absolute value of the differences index, the temporal 
speckle standard deviation index and the temporal 
speckle mean index.
we show that  the dynamic speckle index value decrease your maximum excursion with 
the grow of sampling frequency because this affect directly the time integration 
(exposition time) of camera.
\end{abstract}

\begin{keyword}
Frequency sampling \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)

The dynamic speckle analysis over biological samples has become  currently  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the level of biological activity. 
The importance of technical aspects of dynamic speckle analysis,
as the stability of laser illumination level, was analized \cite{gonzalez2018diode}; 
and was showed as indexes as
the absolute values of the differences \cite{cardoso2014,rivera2017selection} are affected in your values
by the variation of illumination level. Thus, It is necessary analyze the effect
of technical parameters that affect the perceived illumination level; In these sense
analyze the effect of sampling frequency in a dynamic speckle analysis

%2) Exponha qual será o percurso (defina seçoes)
%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
%4) Relevancia do artigo(importancia para outros del artigo publicado)
%5) Anuncie a hipotesi
%6) Anuncie os objetivos (receita pra demostrar a h.)

@@

\subsection{Exposure time of the camera}
\label{subsec:expositiontime}
The acquisition time,  frame per seconds ($fps$) or sampling frequency ($F_s$), 
in the camera Marlin F-033 will be calculated in the 
 Table \ref{table:1}, where we can see, the shutter register value ($Shutter$), 
time base register value ($Base$),
exposure time ($Exposure$),
exposure time offset ($Offset$) and
effective exposure time ($E$); so that 
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to the  $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling frequency}
\label{table:1}
\end{table}

\subsection{Data packages in the ink drying process}
\label{subsec:data1}
 This data package analyze a drying ink process, 
 where images data packages are taken at the times
 $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
 In each time, the package
 has 512 images of 147 pixels of height and 166 pixels of width.
 They were use 4 different sampling frequencies to the images in each package,
 being these frequencies $15$, $30$, $45$ and $60$ hz.

\subsection{Data package of the activity analysis in corn seed}
\label{subsec:data2}
 This data package analyze the activity of a corn seed with 3 days of germination. 
 In this point, 
 They are taken 4 image data packages with different sampling frequencies to each package,
 being these frequencies $15$, $30$, $45$ and $60$ hz.
 Each package has 512 images of $15$ pixels of height and $15$ pixels of width.

\subsection{Test 1: ink drying process}
\label{subsec:test1}
The Fig. \ref{fig:test1} represents the data analysis method, acquired at a 
sampling frequency of $F_s$, 
with the characteristic seen in the Section \ref{subsec:data1},
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test1.eps}
\caption{Data analysis of the ink drying process test.}
\label{fig:test1}
\end{figure}
where, $P(t)$ is an image data package at the time $t$ minutes, 
being that this package has $N$ images and $M$ pixels, where $P_{n,m}(t)$ 
define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
The $MEAN$ block represents the calculus of a temporal speckle mean index from 
the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
The $AVD$ block represents the calculus of an absolute values of the differences index from 
the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
The $STD$ block represents the calculus of a temporal speckle standard deviation index from 
the package $P(t)$, returning the value $STD(t)$, as exposed in the Section \ref{sec:std}.
And finally,
the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
with order $40$ and cut-off at $0.25F_s$ and this block filter the $P(t)$ package and return $Q(t)$,
that causes to have at end of path the $STDF(t)$ index value.
According the information of the data packages, 
we will have speckle indexes values, for each minute during 10 minutes.

\subsection{Test 2: Activity analysis in corn seed}
\label{subsec:test2}
The activity analysis of a corn seed, 
uses the information of data package seen in the Section \ref{subsec:data2}.
We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
with the difference that is taken an data package at the time $t$ (3 days of germination)
and a sampling frequency $F_s$.

@@

The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
acquired  with a sampling frequency of $F_s$. This package pass through the $BPF$ block
described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
according the Eq. \ref{eq:f1f2}, where $l$ represent the band so that $1\leq l\leq L$,
being $L$ the quantity of analysis frequency bands; 
thus, we obtaining the  $R$ package (a filtered version of $P$). Later, It is processed 
a $\sigma$ block, where It is calculate the $\sigma_{m}$ value to each pixel in the package $R$,
as described in the Sec \ref{sec:std}. Finally, 
an image is obtained and It is designed with the variable $STDB$.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test3.eps}
\caption{Frequency band analysis of a data package.}
\label{fig:test3}
\end{figure}

@@

The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:mu},
\begin{equation}\label{eq:mu}
\mu_{m} = \sum \limits_{n=1}^{N} \frac{P_{n,m}}{N}.
\end{equation}
Finally, the $MEAN$ index is the mean value of all $\mu_{m}$ results,
as can be viewed in the Eq. \ref{eq:MEAN},
\begin{equation}\label{eq:MEAN}
MEAN = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
\end{equation}

@@

The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} calculates the mean
value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:avd0},
\begin{equation}\label{eq:avd0}
AVD_{m} = \sum \limits_{n=2}^{N} \frac{|P_{n,m}-P_{n-1,m}|}{N}.
\end{equation}
Finally, the $AVD$ index is the mean value of all $AVD_{m}$ results,
as can be viewed in the Eq. \ref{eq:AVD},
\begin{equation}\label{eq:AVD}
AVD = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
\end{equation}

@@

The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} calculates the standard deviation
value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:sigma},
\begin{equation}\label{eq:sigma}
\sigma_{m}^2 = \sum \limits_{n=1}^{N} \frac{(P_{n,m}-\mu_{m})^2}{N}.
\end{equation}
Finally, the $STD$ index is the mean value of all $\sigma_{m}$ results,
as can be viewed in the Eq. \ref{eq:STD},
\begin{equation}\label{eq:STD}
STD = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Result of test 1}
\label{subsec:resulttest1}
This test shows the analyze result of an ink drying process, across 10 minutes,
with the sampling frequency: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:MEANtest1} analyze the $MEAN(t)$ index,
in the test showed in the Section \ref{subsec:test1},
to each time $t$ for 4 sampling frequencies.
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_f11_rawMEAN.eps}
    \caption{$MEAN$ index value.}\label{fig:MEANtest1}
\end{figure}
It easy to see as the value of index has a monotonous 
behavior over time. By other side the values in the curves decreases in proportion with 
the grow of sampling frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
Section \ref{subsec:test1} about the $AVD(t)$ index.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawAVD.eps}
        \label{fig:avdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1AVD.eps}
        \label{fig:avdnorm}
    \end{subfigure}
    \caption{$AVD$ index anaysis.}\label{fig:AVDtest1}
\end{figure}
The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
to 4 sampling frequencies, showing a different behavior across time in each sampling frequency,
so that, the value of the index in all  the curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
so that the maximum value of curves have an unit value; thus,
It is easy to see that the maximum excursion of the curve is greater when decrease
the sampling frequency. Remembering that this index use information in a frequency
band between $F_s/4$ until $F_s/2$ Hz, as seen in Section \ref{sec:avd}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:STDtest1} analyze the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling frequencies. Remembering that this index uses information in a frequency
band between $0$ until $F_s/2$ Hz, as seen in Section \ref{sec:std}.
This index shows a different behavior across time to each sampling frequency,
so that, the value of the index in each time of curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
It is easy to see that exist a small difference between the maximum excursion 
of the curves with different sampling frequency; even so, It is possible to observe
a decrease of the maximum excursion in the curve with the grow of the sampling frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:STDFtest1}, analyze the $STDF(t)$ index, in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
        \label{fig:stdfraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
        \label{fig:stdfnorm}
    \end{subfigure}
    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
\end{figure}
The Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
to 4 different sampling frequencies. Remembering that this index uses filtered 
information of datapack, so that your frequency
band is between $F_s/4$ and $F_s/2$ Hz, of similar way of $AVD(t)$ index but with
different order filter, as seen in Section \ref{sec:stdf}.
This index shows monotone decreasing behavior in time, where we observe 
a different behavior across time to each different sampling frequency;
so that, the value of the index in each time of curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
being the unit, the maximum value of curves; thus,
It is easy to see that exist a considerable difference between the maximum excursion 
of the curves with the use of sampling frequency; so, It is possible to observe a 
grow of the maximum excursion with the grow of the sampling frequency.

@@

This test shows the analyze result of a corn seed  with 3 days of germination,
with the sampling frequencies: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
in the test described in the Section \ref{subsec:test2};
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALLMEAN.eps}
    \caption{$MEAN$ index value in the germinated corn seed.}\label{fig:MEANtest2}
\end{figure}
The figure shows as the index decrease your value, 
with the increment of sampling frequency in the datapack,
so that between $15$ Hz until $60$ Hz, the index value reaches the $20.137\%$ of your value.

>>>>

\begin{abstract}
In this article, we show as the variation of sampling frequency, 
in a dynamic speckle analysis, affect the value of some dynamic speckle index, 
in this case: the absolute value of the differences index, the temporal 
speckle standard deviation index and the temporal 
speckle mean index.
we show that  the dynamic speckle index value change your maximum excursion with 
the variation of sampling frequency because this affect directly the time integration 
(exposition time) of camera.
We highlight the importance of knowing  the frequency band of analyzed phenomenon, 
to thus can choose the appropriate sampling frequency, 
being recommendable to use the minimal sampling frequency possible
to get an acceptable maximum excursion, 
and an illumination level in the images with good signal-noise relation.

\end{abstract}

\begin{keyword}
Sampling frequency \sep
Dynamic speckle index \sep 
Dynamic speckle index \sep 
Dynamic speckle analysis
\end{keyword}

@@

%1) Anuncie o tema e o problema do artigo (forma de pergunta + definiçoes)
The dynamic laser speckle analysis is  an important
study topic\cite{catalano2019viability,rivera2019sound,gonzalez2018diode,Silva2018,braga2017dynamic} 
to determine the  activity level of biological materials. 
The importance of technical aspects of dynamic laser speckle analysis,
as the stability of laser illumination level has been  analyzed, 
and It was studded the effect of illumination instability over an index value \cite{gonzalez2018diode},
as the absolute values of the differences \cite{cardoso2014,rivera2017selection}, and
It  was showed the dependence between the index value and the illumination level.

%3) Resgate a problematica( Importancia do problema de pesquisa - extenda primer passo)
Thus, 
It is necessary analyze the effect of technical parameters that affect the perceived illumination level; 
in these sense,
we analyze the effect of sampling frequency, 
and consequently the exposure time, in a dynamic laser speckle analysis
that use: the absolute value of the differences index, 
the temporal speckle standard deviation index and the temporal speckle mean index \cite{Nothdurft:05}.

%4) Relevancia do artigo(importancia para outros del artigo publicado)
Knowing the effect of sampling frequency over an index value,
a researcher will be able to have a criteria to choose the appropriate sampling frequency 
for a certain study phenomenon. Thus,
 optimizing resources when choosing the hardware specification in a system setup; 
being in this case, the limitations relatives to illumination level and signal-noise relation in the study sample.

%5) Anuncie a hipotesis
For this purpose, we show that give a dynamic speckle test, exist a appropriate frequency band
to choose the sampling frequency, and that to use high values of this parameters
may to have unintended consequences on the index value, 
as the decrease of the excursion between two activity levels, given a determinate index value. 
by other side we known by other work \cite{Nothdurft:05}; 
that decreasing the sampling frequency, and consequently increase the exposure time,
reduce the image contrast in a processed test and consequently limit the possibility
of to get information about the inside of the sample.

%6) Anuncie os objetivos (receita pra demostrar a h.)
To be able to demonstrate the existence of this appropriate frequency band,
we will perform two types of tests, in the first we analyze a  ink drying process along the time; and
the second test analyze, in a determinate time, the activity state of a corn seed, with 3 days of germination.
In both case are used 4 different sampling frequencies, 
and are compared the behavior of used speckle indexes.

%2) Exponha qual será o percurso (defina seçoes)
In the next section we describe how the speckle images were acquired and the setup used to analyze them; 
all theoretical definitions, necessary to understand the analysis, will shown in the Section 3;
numerical results of the analysis  are presented in Section 4, and
an analysis of the results is reported in the Section 5; finally, we present our
conclusion in the Section 6.

@@

\subsection{Exposure time of the camera}
\label{subsec:expositiontime}
The sampling frequency ($F_s$) or acquisition time, frame per seconds ($fps$), 
in the camera Marlin F-033 is calculated in the 
 Table \ref{table:1}, 
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 $Shutter$ &  $Base$ [$\mu s$] & $Offset$ [$\mu s$] & $E$ [$ms$] & $F_s$ [$fps$]\\ [0.5ex] 
 \hline\hline
 3332  & 20  & 12  & 66.652  & 15.003  \\ 
 1665  & 20  & 12  & 33.312  & 30.019  \\ 
 1110  & 20  & 12  & 22.212  & 45.021  \\ 
 832   & 20  & 12  & 16.652  & 60.053  \\ [1ex] 
 \hline
\end{tabular}
\caption{Exposition time and sampling frequency}
\label{table:1}
\end{table}
where we can see the 4 sampling frequencies used in the tests, the shutter register value ($Shutter$), 
time base register value ($Base$),
exposure time ($Exposure$),
exposure time offset ($Offset$) and
effective exposure time ($E$); so that 
\begin{equation}
Exposure= Shutter \times Base,
\end{equation}
\begin{equation}
\frac{1}{F_s}=E= Exposure + Offset.
\end{equation}
Where,  $F_s$ is calculated in relation to the  $E$; being that,
the $Exposure$ represent the photography integration time and $E$ the effective time
between photographs; 
the difference between these two exposures arise from $Offset$ time, 
that is the time between end and start of a photography.
In all cases the exposure time is much bigger than $Offset$, so we can approximate
that $F_s\approx 1/Exposure$.

\subsection{Data packages in the ink drying process}
\label{subsec:data1}
 This set of data  analyze a drying ink process, 
 where group of images (data package) are taken at the times
 $\{0,$ $1,$ $2,$ $3,$ $4,$ $5,$ $6,$ $7,$ $8,$ $9,$ $10\}$ min. 
 In each time, a package
 has 512 images of 147 pixels of height and 166 pixels of width.
 They were use 4 different sampling frequencies to take the images,
 being these frequencies $15$, $30$, $45$ and $60$ hz.

\subsection{Data package of the activity analysis in corn seed}
\label{subsec:data2}
 This data package analyze the activity of a corn seed with 3 days of germination. 
 In this seed are taken 4 image data packages with different sampling frequencies to each package,
 being these frequencies $15$, $30$, $45$ and $60$ hz.
 Each package has 512 images of $15$ pixels of height and $15$ pixels of width.

\subsection{Test 1: ink drying process}
\label{subsec:test1}
The Fig. \ref{fig:test1} represents the data analysis method, 
to given  $F_s$ sampling frequency, 
with a sample of the characteristic described in the Section \ref{subsec:data1}.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test1.eps}
\caption{Data analysis of the ink drying process test.}
\label{fig:test1}
\end{figure}
Where, $P(t)$ is an image data package at the time $t$ minutes, 
being that this package has $N$ images and $M$ pixels; $P_{n,m}(t)$ 
define the $n$-th image and $m$-th pixel, for all $1 \leq n \leq N$, $1 \leq m \leq M$.
The $MEAN$ block represents the calculus of a temporal speckle mean index on 
the package $P(t)$, returning the value $MEAN(t)$, as exposed in the Section \ref{sec:mean}. 
The $AVD$ block represents the calculus of an absolute values of the differences index on
the package $P(t)$, returning the value $AVD(t)$, as exposed in the Section \ref{sec:avd}. 
The $STD$ block represents the calculus of a temporal speckle standard deviation index on 
the package $P(t)$ or $Q(t)$, returning the value $STD(t)$ or $STDF(t)$, respectively; as exposed in the Section \ref{sec:std}.
And finally,
the block $HPF$ represents a digital finite impulse response ``high-pass filter'' 
with order $40$ and cut-off at $0.25F_s$ and this block filter the $P(t)$ package and return $Q(t)$,
that causes to have at end of path the $STDF(t)$ index value.
According the information of the data packages, 
we will have speckle indexes values, for each minute, during 10 minutes.

\subsection{Test 2: Activity analysis in corn seed}
\label{subsec:test2}
The activity analysis of a corn seed, 
uses the information of data package seen in the Section \ref{subsec:data2}.
We analyze this information of similar way to the seen in the Section \ref{subsec:test1},
with the difference that is taken an data package only at the time $t$ (3 days of germination).

@@

The Fig. \ref{fig:test3} represents the frequency band analysis method of data package $P$, 
acquired  with a sampling frequency of $F_s$. This package pass through the $BPF$ block
described in the Sec \ref{sec:stdb}, with a frequency band pass between $f_1(l)$ and $f_2(l)$,
where $l$ represent the band so that $1\leq l\leq L$,
being $L$ the quantity of analysis frequency bands; 
thus, we obtaining the  $R$ package (a filtered version of $P$). Later, It is processed 
a $\sigma$ block, where It is calculate the $\sigma_{m}$ value to each pixel in the package $R$,
as described in the Sec \ref{sec:std}. Finally, 
an image is obtained and It is designed with the variable $STDB$.
\begin{figure}[ht!]
\centering
\includegraphics[width=0.55\columnwidth]{test3.eps}
\caption{Frequency band analysis of a data package.}
\label{fig:test3}
\end{figure}

@@

The temporal speckle mean index ($\mu_{m}$) \cite{Nothdurft:05} calculates the mean
value of the illumination level to the $m$-th pixel in the package $P$, and It is implemented
with the Eq. \ref{eq:mu},
\begin{equation}\label{eq:mu}
\mu_{m} = \sum \limits_{n=1}^{N} \frac{P_{n,m}}{N}.
\end{equation}
Finally, the $MEAN(t)$ index is the mean value of all $\mu_{m}$ results,
as can be viewed in the Eq. \ref{eq:MEAN},
\begin{equation}\label{eq:MEAN}
MEAN(t) = \sum \limits_{m=1}^{M} \frac{\mu_{m}}{M}.
\end{equation}

@@

The Absolute Values of the Differences ($AVD_{m}$) \cite{cardoso2014,rivera2017selection} calculates the mean
value of the absolute differences in the illumination level of the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:avd0},
\begin{equation}\label{eq:avd0}
AVD_{m} = \sum \limits_{n=2}^{N} \frac{|P_{n,m}-P_{n-1,m}|}{N}.
\end{equation}
Finally, the $AVD(t)$ index is the mean value of all $AVD_{m}$ results,
as can be viewed in the Eq. \ref{eq:AVD},
\begin{equation}\label{eq:AVD}
AVD(t) = \sum \limits_{m=1}^{M} \frac{AVD_{m}}{M}
\end{equation}

@@

The temporal speckle standard deviation index ($\sigma_{m}$) \cite{Nothdurft:05} calculates the standard deviation
value of the illumination level to the $m$-th pixel in the package $P$, It is implemented
with the Eq. \ref{eq:sigma},
\begin{equation}\label{eq:sigma}
\sigma_{m}^2 = \sum \limits_{n=1}^{N} \frac{(P_{n,m}-\mu_{m})^2}{N}.
\end{equation}
Finally, the $STD(t)$ index is the mean value of all $\sigma_{m}$ results,
as can be viewed in the Eq. \ref{eq:STD},
\begin{equation}\label{eq:STD}
STD(t) = \sum \limits_{m=1}^{M} \frac{\sigma_{m}}{M}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Result of test 1}
\label{subsec:resulttest1}
This test shows the analyze result of an ink drying process, across 10 minutes,
using the sampling frequencies: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:MEANtest1} analyze the $MEAN(t)$ index,
in the test showed in the Section \ref{subsec:test1},
to each time $t$ for the  4 sampling frequencies.
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_f11_rawMEAN.eps}
    \caption{$MEAN$ index value.}\label{fig:MEANtest1}
\end{figure}
It easy to see as the value of index has a monotonous 
behavior over time. By other side the values in the curves decreases in proportion with 
the grow of sampling frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:AVDtest1} shows the result of analysis explained in the 
Section \ref{subsec:test1} about the $AVD(t)$ index.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawAVD.eps}
        \label{fig:avdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $AVD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1AVD.eps}
        \label{fig:avdnorm}
    \end{subfigure}
    \caption{$AVD$ index anaysis.}\label{fig:AVDtest1}
\end{figure}
The Figure \ref{fig:avdraw} shows the $AVD(t)$ index, in each time $t$, 
to 4 sampling frequencies, showing a different behavior across time in each sampling frequency,
so that, the value of the index in all  the curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:avdnorm} shows a normalized version of $AVD(t)$ index, 
so that the maximum value of curves have an unit value; thus,
It is easy to see that the maximum excursion of the curve is greater when decrease
the sampling frequency. Remembering that this index use information in a frequency
band between $F_s/4$ until $F_s/2$ Hz \cite{rivera2017selection}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:STDtest1} analyze the $STD(t)$ index in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTD.eps}
        \label{fig:stdraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STD$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STD.eps}
        \label{fig:stdnorm}
    \end{subfigure}
    \caption{$STD$ index anaysis.}\label{fig:STDtest1}
\end{figure}
The Figure \ref{fig:stdraw} shows the  behavior of $STD(t)$ index, in each time $t$, 
to 4 different sampling frequencies. Remembering that this index uses information in the entire frequency
band ($0$ until $F_s/2$ Hz), as seen in Section \ref{sec:std}.
This index shows a different behavior across time to each sampling frequency,
so that, the value of the index in each time of curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:stdnorm} shows a normalized version of $STD(t)$ index;
being the unit, the maximum value of curves; thus,
It is easy to see that exist a small difference between the maximum excursion 
of the curves with different sampling frequency; even so, It is possible to observe
a slight decrease of the maximum excursion in the curve with the grow of the sampling frequency, 
unlike the $AVD(t)$ index.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:STDFtest1}, analyze the $STDF(t)$ index, in the test showed in the 
Section \ref{subsec:test1}.
\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \caption{$STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_rawSTDF.eps}
        \label{fig:stdfraw}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}{0.48\textwidth}
        \caption{Normalized $STDF$ index value.}
        \includegraphics[width=\textwidth]{FPS_f11_norm1STDF.eps}
        \label{fig:stdfnorm}
    \end{subfigure}
    \caption{$STDF$ index anaysis.}\label{fig:STDFtest1}
\end{figure}
The Figure \ref{fig:stdfraw} shows the behavior $STDF(t)$ index, in each time $t$, 
to 4 different sampling frequencies. Remembering that this index uses filtered 
information of datapack, so that your frequency
band is between $F_s/4$ and $F_s/2$ Hz, of similar way of $AVD(t)$ index but with
different order filter, as seen in Section \ref{sec:stdf}.
This index shows monotone decreasing behavior in time, where we observe 
a different behavior across time to each different sampling frequency;
so that, the value of the index in each time of curve decreases in proportion with 
the grow of sampling frequency. By other side,
the Figure \ref{fig:stdfnorm} shows a normalized version of $STDF(t)$ index;
being the unit, the maximum value of curves; thus,
It is easy to see that exist a considerable difference between the maximum excursion 
of the curves with the use of sampling frequency; so, It is possible to observe a 
grow of the maximum excursion with the grow of the sampling frequency, like the $AVD(t)$ index.

@@

This test shows the analyze result of a corn seed  with 3 days of germination,
with images acquires using the sampling frequencies: $15$, $30$, $45$ and $60$Hz.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:MEANtest2} shows the $MEAN(t)$ index,
in the test described in the Section \ref{subsec:test2};
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALLMEAN.eps}
    \caption{$MEAN$ index value in the germinated corn seed.}\label{fig:MEANtest2}
\end{figure}
We observe as the index decrease your value, 
with the increment of sampling frequency in the datapack,
so that between $15$ Hz until $60$ Hz, the index value reaches the $20.137\%$ of your value.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Figure \ref{fig:INDEXtest2} shows the $AVD(t)$, $STD(t)$ and $STDF(t)$ indexes,
in the test described in the Section \ref{subsec:test2};
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{FPS_Semilla_3_3diasALL.eps}
    \caption{$AVD(t)$, $STD(t)$ and $STDF(t)$ indexes values in the germinated corn seed.}\label{fig:INDEXtest2}
\end{figure}
The similar way that in the Figure \ref{fig:MEANtest2},
the index decrease your value with the grow of $F_s$,
so that the indexes, 
$STD(t)$, $AVD(t)$  and $STDF(t)$, 
reaches the $22.2426\%$, $19.2578\%$ and $20.3541\%$ of your values, 
respectively.
